### 2023-10-17 main.tex
Bozza

The product $\left(\mathcal{S}_{2}^{-1}\right)^{\otimes L}|\Psi^{''}\rangle$ gives a vector $|\Psi^{'}\rangle$ whose component are denoted by $\Psi^{'}(\bm{\tau})$. 
To find these quantities we need to fix the rows correspondent to $\bm{\tau}$ in the matrix $\left(\mathcal{S}_{2}^{-1}\right)^{\otimes L}$. Consider a string $\bm{\tau}=(\tau_{1},\ldots,\tau_{L})$ with $\tau_{1},\ldots,\tau_{L}\in \{1,\ldots,N\}$, then the corresponding row reads
\left(\mathcal{S}_{2}^{-1}\right)^{\otimes L}_{\bm{\tau}}&=\,e_{\tau_{1},\ldots,\tau_{L}}^{\tau_{1},\ldots,\tau_{L}}+\sum_{q_{1}=1}^{L}(1-\delta_{\tau_{q_{1}},N})e_{\tau_{1},\ldots,\tau_{L}}^{\varphi_{1}^{1},\ldots,\varphi_{L}^{1}}\beta_{\tau_{q_{1}}}\\&+\sum_{q_{1},q_{2}=1\,:\,q_{1}\neq q_{2}}^{L}(1-\delta_{\tau_{q_{1}},N})(1-\delta_{\tau_{q_{2}},N})e_{\tau_{1},\ldots,\tau_{L}}^{\varphi_{1}^{2},\ldots,\varphi_{L}^{2}}\beta_{\tau_{q_{1}}}\beta_{\tau_{q_{2}}}
  \ldots+\sum_{q_{1},\ldots,q_{L}=1\,:\,q_{i}\neq q_{j}\;\text{if}\;i\neq j}^{L}\left(\prod_{x=1}^{L}(1-\delta_{\tau_{x},N})\right)\left(\beta_{\tau_{x}}\right)^{1-\delta_{\tau_{x},1}}e_{\tau_{1},\ldots,\tau_{L}}^{\varphi_{1}^{L},\ldots,\varphi_{L}^{L}}
%Now we can write the ground state of $H^{''}$ as \begin{equation}|\Psi^{''}\rangle=\sum_{\mu_{1},\ldots,\mu_{L}=1}^{N}\Psi^{''}(\bm{\mu})|\bm{\mu}\rangle\end{equation} with the coefficients $\psi^{''}(\bm{\mu})$ are given in \eqref{coefficients-psiSec}.
%Therefore, we have that equation \eqref{ABS_intermediate} becomes
%Because of the exponent $(1-\delta_{\tau_{x},1})$, the element $\Psi^{''}(\bm{\tau})$ has, up the term $\frac{\Gamma(2+\sum_{i=1}^{L}\delta_{\tau_{x},1})}{\Gamma(L+2)}$, a contribution of a factor $\lambda_{\tau_{x}}\left(2+L-x-\sum_{j=x}^{L}(1-\delta_{\tau_{x},1})\right)$ if the site is non empty, and a contribution of a factor "$1$" if the site is empty, it is convenient to introduce the $c_{i}$ of defined in \eqref{CiEquation}. Then, equation  \eqref{ABS_intermediate} reads 
Therefore, using equation \eqref{ABS_intermediate}, we obtain 
\begin{equation}\label{elementsABS}
		\Psi^{'}(\bm{\tau})=\sum_{c_{1}=0}^{1-\delta_{\tau_{1},N}}\ldots\sum_{c_{L}=0}^{1-\delta_{\tau_{L},N}}\frac{\Gamma(2+L-\sum_{x=1}^{L}c_{x})}{\Gamma(2+L)}\prod_{x=1}^{L}\left(\lambda_{\tau_{x}}\left(2+L-x-\sum_{j=x}^{L}c_{j}\right)\right)^{c_{x}}\left(\beta_{\tau_{x}}\right)^{(1-c_{x})(1-\delta_{\tau_{x},N})}\dt
%Indeed, when $c_{i}=0$ this formula replaces the contribution in the square brackets with a $\beta_{\tau_{x}}$. 
Finally, considering all possible $\tau_{1},\ldots,\tau_{L}\in \{1,\ldots,N\}$, we obtain \eqref{ABS-vect}.

@@

\paragraph{Proof of formula \eqref{exactCorrelations}} Consider $m$ particles of non-empty types $s_{i}\in\{1,\ldots,N-1\}$ in positions $y_{i}\in\{1,\ldots,L\}$ such that $y_{i}<y_{i+1}$ for all $i=1,\ldots,m$. We aim to compute the non-equilibrium stationary state correlation $\langle n_{s_{1}}^{y_{1}}\cdots n_{s_{m}}^{y_{m}} \rangle_{stat}$. By using duality, we showed in \eqref{CorrelationByABS-prob} that
 	\langle n_{s_{1}}^{y_{1}}\cdots n_{s_{m}}^{y_{m}} \rangle_{stat}=\langle\hat{\bm{\xi}}\rangle_{stat,dual}
where $\langle\hat{\bm{\xi}}\rangle_{stat,dual}$ we have denoted the stationary state of the dual process starting from the configuration $\hat{\bm{\xi}}$. 
Using formula \eqref{ABS} for a configuration where all $\tau_{y_{i}}=s_{i}$  for $i=1,\ldots,m$ and $\tau_{j}=N$ for $j\in\{1,\ldots,L\}\setminus \{y_{1},\ldots,y_{m}\}$, we obtain 
 \langle\hat{\bm{\xi}}\rangle_{stat,dual}=\Psi^{'}(\tau_{1},\ldots,\tau_{L})=\sum_{c_{1}=0}^{1}\ldots\sum_{c_{L}=0}^{1}\frac{\Gamma(2+L-\sum_{a=1}^{m}c_{k})}{\Gamma(2+L)}\prod_{k=1}^{m}\lambda_{\tau_{k}}^{c_{k}}\beta_{\tau_{k}}^{1-c_{k}}\left(2+L-y_{k}-\sum_{j=k}^{m}c_{j}\right)^{c_{k}}\dt

@@

\textbf{Remark}: the first and second cumulants, computed in \eqref{one-pts-corr} and \eqref{two-pts-corr} respectively, match with the ones found in Subsection 4.3 of \cite{vanicat2017exact}. \\ \\
\textbf{How $|\Psi^{'}\rangle$ is related to steady state non-equilibrium correlations and to absorption probabilities?}\\
We aim to compute correlations between non-empty species in the steady state. We know that for any chain length $L$ we have that the steady state $|\Psi\rangle$ is related to $|\Psi^{'}\rangle$ by
	|\Psi\rangle=\left(\mathcal{S}_{1}^{-1}\right)^{\otimes L}|\Psi^{'}\rangle
We aim to compute the correlations between non-empty particles of an arbitrary configuration $\bm{\tau}$.
This is equivalent to consider a shorter chain where only non-empty particles are left, while all the sites occupied by the empty $N$ are removed. 
This chain has length $m=\sum_{x=1}^{L}(1-\delta_{\tau_{x},N})$, where all these $m$ sites are occupied by particles of species for $1$ to $N-1$. To find the desired correlations we compute the steady state of this shorter chain. We denote its configuration chain by $\widehat{\bm{\tau}}$. This configuration is obtained from $\bm{\tau}$ by re-labelling properly the occupations from $1$ to $m$. Then, these $m$ point correlations can be computed by finding $\Psi(\widehat{\bm{\tau}})$.\\ \\ To clarify consider the example $N=3$ and $L=4$ where the empty is the species $3$. Take a configuration  
	\bm{\tau}=(\tau_{1}=2,\tau_{2}=3,\tau_{3}=1,\tau_{4}=3)
What is the correlation between the occupied species? To compute this we can define the new chain of length $m=2$ with the configuration $\widehat{\bm{\tau}}=(\widehat{\tau}_{1}=2,\widehat{\tau}_{2}=1)$ and find the steady state $|\Psi\rangle$ of this shorter chain. \\ \\
To compute the steady state of the shorter chain we can use the result that we have in the appendix A in equation \eqref{Tensor-S1}:
		\langle \bm{\tau}|	\left(\mathcal{S}_{1}^{-1}\right)^{\otimes L}|\bm{\mu}\rangle=\prod_{x=1}^{L}\left(\delta_{\mu_{x},\tau_{x}}+(-1)\delta_{\tau_{x},N}\sum_{i_{x}=1}^{N-1}\delta_{\mu_{x},i_{x}}\right)
Thus, for the shorter chain we have that 
	\langle \widehat{\bm{\tau}}|\left(\mathcal{S}_{1}^{-1}\right)^{\otimes L}|\bm{\mu}\rangle=\prod_{x=1}^{m}\left(\delta_{\mu_{x},\tau_{x}}\right)
this implies that 
	\Psi(\widehat{\bm{\tau}})=\Psi^{'}(\widehat{\bm{\tau}})
where here both $|\Psi(\widehat{\bm{\tau}})\rangle$ and $|\Psi^{'}(\widehat{\bm{\tau}})\rangle$ are eigenvector with vanishing eigenvalue of chains of length $m$. 
We have computed this $\Psi^{'}(\widehat{\bm{\tau}})$ in \eqref{exactCorrelations} as
	\Psi^{'}(\widehat{\bm{\tau}})\sum_{c_{1},\ldots,c_{m}=0}^{1}
We also know from \eqref{CorrelationByABS-prob} that 
	\Psi(\widehat{\bm{\tau}})= \sum_{c_{1}=0}^{1}\ldots \sum_{c_{m}=0}^{1}\prod_{k=1}^{m}\alpha_{a_{k}}^{c_{k}}\beta_{a_{k}}^{1-c_{k}}\mathcal{P}(c_{1},\ldots,c_{m},\hat{\bm{\xi}})
therefore, we can read off the absorption probabilities. \\ \\
This argument can be adapted for any $1\leq m\leq L$ to compute $m$-point correlations between non-empty species.\\ \\ 
In general $|\Psi^{'}\rangle$ is the eigenvector with vanishing eigenvalue of $H^{'}$, but I believe it cannot be interpreted directly as a steady state, since $H^{'}$ is not a Markov matrix. However, it gives by the previous argument the exact correlations and as a consequence the absorption probabilities...

>>>>

The product $\left(\mathcal{S}_{2}^{-1}\right)^{\otimes L}|\Psi^{''}\rangle$ gives a vector $|\Psi^{'}\rangle$ whose component are denoted by $\Psi^{'}(\bm{\tau})$. 
To find these quantities we need to fix the rows correspondent to $\bm{\tau}$ in the matrix $\left(\mathcal{S}_{2}^{-1}\right)^{\otimes L}$. Consider a string $\bm{\tau}=(\tau_{1},\ldots,\tau_{L})$ with $\tau_{1},\ldots,\tau_{L}\in \{1,\ldots,N\}$, then the corresponding row reads
\begin{equation}
	\begin{split}
\left(\mathcal{S}_{2}^{-1}\right)^{\otimes L}_{\bm{\tau}}&=\,e_{\tau_{1},\ldots,\tau_{L}}^{\tau_{1},\ldots,\tau_{L}}+\sum_{q_{1}=1}^{L}(1-\delta_{\tau_{q_{1}},N})e_{\tau_{1},\ldots,\tau_{L}}^{\varphi_{1}^{1},\ldots,\varphi_{L}^{1}}\beta_{\tau_{q_{1}}}\\&+\sum_{q_{1},q_{2}=1\,:\,q_{1}\neq q_{2}}^{L}(1-\delta_{\tau_{q_{1}},N})(1-\delta_{\tau_{q_{2}},N})e_{\tau_{1},\ldots,\tau_{L}}^{\varphi_{1}^{2},\ldots,\varphi_{L}^{2}}\beta_{\tau_{q_{1}}}\beta_{\tau_{q_{2}}}
  \\&+
  \ldots+\sum_{q_{1},\ldots,q_{L}=1\,:\,q_{i}\neq q_{j}\;\text{if}\;i\neq j}^{L}\left(\prod_{x=1}^{L}(1-\delta_{\tau_{x},N})\right)\left(\beta_{\tau_{x}}\right)^{1-\delta_{\tau_{x},1}}e_{\tau_{1},\ldots,\tau_{L}}^{\varphi_{1}^{L},\ldots,\varphi_{L}^{L}}
	\end{split}
\end{equation}
\end{comment}
%Now we can write the ground state of $H^{''}$ as \begin{equation}|\Psi^{''}\rangle=\sum_{\mu_{1},\ldots,\mu_{L}=1}^{N}\Psi^{''}(\bm{\mu})|\bm{\mu}\rangle\end{equation} with the coefficients $\psi^{''}(\bm{\mu})$ are given in \eqref{coefficients-psiSec}.
%Therefore, we have that equation \eqref{ABS_intermediate} becomes
%Because of the exponent $(1-\delta_{\tau_{x},1})$, the element $\Psi^{''}(\bm{\tau})$ has, up the term $\frac{\Gamma(2+\sum_{i=1}^{L}\delta_{\tau_{x},1})}{\Gamma(L+2)}$, a contribution of a factor $\lambda_{\tau_{x}}\left(2+L-x-\sum_{j=x}^{L}(1-\delta_{\tau_{x},1})\right)$ if the site is non empty, and a contribution of a factor "$1$" if the site is empty, it is convenient to introduce the $c_{i}$ of defined in \eqref{CiEquation}. Then, equation  \eqref{ABS_intermediate} reads 
Therefore, using equation \eqref{ABS_intermediate}, we obtain 
\begin{equation}\label{elementsABS}
	\begin{split}
		\Psi^{'}(\bm{\tau})=\sum_{c_{1}=0}^{1-\delta_{\tau_{1},N}}\ldots\sum_{c_{L}=0}^{1-\delta_{\tau_{L},N}}\frac{\Gamma(2+L-\sum_{x=1}^{L}c_{x})}{\Gamma(2+L)}\prod_{x=1}^{L}\left(\lambda_{\tau_{x}}\left(2+L-x-\sum_{j=x}^{L}c_{j}\right)\right)^{c_{x}}\left(\beta_{\tau_{x}}\right)^{(1-c_{x})(1-\delta_{\tau_{x},N})}\dt
	\end{split}
\end{equation} 
%Indeed, when $c_{i}=0$ this formula replaces the contribution in the square brackets with a $\beta_{\tau_{x}}$. 
Finally, considering all possible $\tau_{1},\ldots,\tau_{L}\in \{1,\ldots,N\}$, we obtain \eqref{ABS-vect}.
\begin{flushright}
    $\square$
\end{flushright}

\subsection{Explicit formula for the steady state $|\Psi\rangle$}
The steady state $|\Psi\rangle$ of the Hamiltonian $H$ is given by 
\begin{equation}\label{steadyStateH}
	|\Psi\rangle=\sum_{\tau_{1},\ldots,\tau_{L}=1}^{N}\Psi(\bm{\tau})|\bm{\tau}\rangle
where for every $(\tau_{1},\ldots,\tau_{L})=\bm{\tau}$
\begin{equation}\label{SteadyState-coeff-implicit}
		\Psi(\bm{\tau})=&\Psi^{'}(\bm{\tau})\\+&\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{i_{q_{1}}=1}^{N-1}\ldots\sum_{i_{q_{b}}=1}^{N-1}\Psi^{'}(\tau_{1},\ldots,\underbrace{i_{q_{1}}}_{q_{1}},\ldots,\underbrace{i_{q_{b}}}_{q_{b}},\ldots,\tau_{L})
To compute correlations it is enough the above expression, however using \eqref{ABS} it is possible to write $\Psi(\bm{\tau})$ explicitly, see Appendix \ref{appB}.\\
The state $|\Psi\rangle$ is normalized. To prove it we aim to show that 
	\sum_{\bm{\tau}\in\Omega}\langle \bm{\tau}|\Psi\rangle=\sum_{\bm{\tau}\in \Omega}\Psi(\bm{\tau})=1
\textbf{Proof of the normalization}: we aim to show that 
		\sum_{\bm{\tau}\in \Omega}\Psi(\bm{\tau})=&\sum_{\bm{\tau}\in \Omega}\Psi^{'}(\bm{\tau})\nonumber\\+&\sum_{\bm{\tau}\in \Omega}\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{i_{q_{1}}=1}^{N-1}\ldots\sum_{i_{q_{b}}=1}^{N-1}\Psi^{'}(\tau_{1},\ldots,\underbrace{i_{q_{1}}}_{q_{1}},\ldots,\underbrace{i_{q_{b}}}_{q_{b}},\ldots,\tau_{L})\nonumber\\=&1
We introduce an index $\ell\in \{0,\ldots,L\}$ that represents the number of empty occupations for an arbitrary $\bm{\tau}$, i.e. $\ell=\sum_{x=1}^{L}\delta_{\tau_{x},N}$. Moreover, we introduce the space 
	\Omega_{\ell}=\left\{\bm{\tau}\in \Omega\;:\;\sum_{x=1}^{L}\delta_{\tau_{x},N}=\ell\right\}
Therefore, we can rewrite the normalization condition as 
	&\sum_{\ell=0}^{L}\sum_{\bm{\tau}\in \Omega_{\ell}}\Psi^{'}(\bm{\tau})\nonumber
	+\\&\sum_{\ell=0}^{L}\sum_{\bm{\tau}\in \Omega_{\ell}}\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{i_{q_{1}}=1}^{N-1}\ldots\sum_{i_{q_{b}}=1}^{N-1}\Psi^{'}(\tau_{1},\ldots,\underbrace{i_{q_{1}}}_{q_{1}},\ldots,\underbrace{i_{q_{b}}}_{q_{b}},\ldots,\tau_{L})\nonumber\\=&1
We first observe that, using \eqref{ABS}, we have that 
	\Psi^{'}(N,\ldots,N)=1\co
thus we have that it is enough to prove that
	&\sum_{\ell=0}^{L-1}\sum_{\bm{\tau}\in \Omega_{\ell}}\Psi^{'}(\bm{\tau})\nonumber
	+\\&\sum_{\ell=0}^{L}\sum_{\bm{\tau}\in \Omega_{\ell}}\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{i_{q_{1}}=1}^{N-1}\ldots\sum_{i_{q_{b}}=1}^{N-1}\Psi^{'}(\tau_{1},\ldots,\underbrace{i_{q_{1}}}_{q_{1}},\ldots,\underbrace{i_{q_{b}}}_{q_{b}},\ldots,\tau_{L})\nonumber\\=&0
We now consider the second term of the above expression. For any fixed $\ell$ and for any fixed $\bm{\tau}\in \Omega_{\ell}$, $b$ empty occupations are replaced by all possible non-empty species. For a fixed $b$, if the configuration $\bm{\tau}\in \Omega_{\ell}$ with has $\ell<b$, then the this term do not produce any contribution. On the other hand, if $b\geq \ell$ we obtain from $\bm{\tau}$ all possible configuration in the space $ \Omega_{\ell-b}$. Each of such a configuration is counted $\binom{L-\ell+b}{b}$. By calling $r=\ell-b$ if $b\leq \ell$ we have that 
&\sum_{\ell=0}^{L}\sum_{\bm{\tau}\in \Omega_{\ell}}\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{i_{q_{1}}=1}^{N-1}\ldots\sum_{i_{q_{b}}=1}^{N-1}\Psi^{'}(\tau_{1},\ldots,\underbrace{i_{q_{1}}}_{q_{1}},\ldots,\underbrace{i_{q_{b}}}_{q_{b}},\ldots,\tau_{L})\nonumber\\
=&\sum_{b=1}^{L}(-1)^{b}\sum_{r=0}^{L-b}\binom{L-r}{b}\sum_{\bm{\tau}\in \Omega_{r}}\Psi^{'}(\bm{\tau})\mathbbm{1}_{\{b\leq L-r\}}\dt
As a consequence, we have that the normalization condition reads
\sum_{\ell=0}^{L-1}\sum_{\bm{\tau}\in \Omega_{\ell}}\Psi^{'}(\bm{\tau})+\sum_{b=1}^{L}(-1)^{b}\sum_{\ell=0}^{L-b}\binom{L-\ell}{b}\sum_{\bm{\tau}\in \Omega_{\ell}}\Psi^{'}(\bm{\tau})\mathbbm{1}_{\{b\leq L-\ell\}}=0\dt
By exchanging the summations we have 
\sum_{\ell=0}^{L-1}\sum_{\bm{\tau}\in \Omega_{\ell}}\Psi^{'}(\bm{\tau})+\sum_{\ell=0}^{L-1}\sum_{b=1}^{L-\ell}(-1)^{b}\binom{L-\ell}{b}\sum_{\bm{\tau}\in \Omega_{\ell}}\Psi^{'}(\bm{\tau})\mathbbm{1}_{\{b\leq L-\ell\}}=0\dt
It is enough to prove that, for any fixed $\ell\in\{0,\ldots, L-1\}$ we have that 
	1+\sum_{b=1}^{L-\ell}(-1)^{b}\binom{L-\ell}{b}=0
This is true because of the Binomial theorem, indeed 
1+\sum_{b=1}^{L-\ell}(-1)^{b}\binom{L-\ell}{b}=\sum_{b=0}^{L-\ell}(-1)^{b}\binom{L-\ell}{b}=(1-1)^{L-\ell}=0
that implies the normalization of the state $|\Psi\rangle$. 

@@

We aim to compute
\langle n^{y_{1}}_{s_{1}}\cdots n^{y_{m}}_{s_{m}}\rangle_{\text{stat}}=\mathbb{E}_{stat}\left[\prod_{i=1}^{m}\mathbbm{1}_{\{\tau_{y_{i}}=s_{i}\}}\right]=\sum_{\bm{\tau}\in \Omega}\left(\prod_{i=1}^{m}\mathbbm{1}_{\{\tau_{y_{i}}=s_{i}\}}\right)\langle\bm{\tau}|\Psi\rangle=\sum_{\bm{\tau}\in \Omega}\left(\prod_{i=1}^{m}\mathbbm{1}_{\{\tau_{y_{i}}=s_{i}\}}\right)\Psi(\bm{\tau})
We introduce the space 
	\widehat{\Omega}^{m}=\left\{\bm{\tau}\in \Omega\;:\; \tau_{y_{1}}=s_{1},\ldots,\tau_{y_{m}}=s_{m}\right\}
where $m$ occupations are fixed and the other $L-m$ can vary in all possible ways. Therefore, we need to compute 
\langle n^{y_{1}}_{s_{1}}\cdots n^{y_{m}}_{s_{m}}\rangle_{\text{stat}}=\sum_{\bm{\tau}\in \widehat{\Omega}^{m}}\Psi(\tau)
Using \eqref{SteadyState-coeff-implicit}, we have that 
&\sum_{\bm{\tau}\in \widehat{\Omega}^{m}}\Psi(\tau)= \sum_{\bm{\tau}\in \widehat{\Omega}^{m}}\Psi^{'}(\tau)\nonumber
\\+&
\sum_{\bm{\tau}\in \widehat{\Omega}^{m}}\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{i_{q_{1}}=1}^{N-1}\ldots\sum_{i_{q_{b}}=1}^{N-1}\Psi^{'}(\tau_{1},\ldots,\underbrace{i_{q_{1}}}_{q_{1}},\ldots,\underbrace{i_{q_{b}}}_{q_{b}},\ldots,\tau_{L})
We introduce an index $\ell\in \{0,\ldots, L-m\}$ that denotes the number of empty occupations in an arbitrary configuration $\bm{\tau}\in \widehat{\Omega}^{m}$, i.e. $\ell=\sum_{x=1}^{L}\delta_{\tau_{x},N}$. We also introduce the space 
\widehat{\Omega}^{m}_{\ell}=\left\{\bm{\tau}\in \widehat{\Omega}^{m}\;:\;\sum_{x=1}^{L}\delta_{\tau_{x},N}=\ell\right\}
Then we obtain that 
&\sum_{\bm{\tau}\in \widehat{\Omega}^{m}}\Psi(\tau)= \sum_{\ell=0}^{L-m}\sum_{\bm{\tau}\in \widehat{\Omega}^{m}_{\ell}}\Psi^{'}(\tau)\nonumber
\\+&
\sum_{\ell=0}^{L-m}\sum_{\bm{\tau}\in \widehat{\Omega}^{m}_{\ell}}\sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{i_{q_{1}}=1}^{N-1}\ldots\sum_{i_{q_{b}}=1}^{N-1}\Psi^{'}(\tau_{1},\ldots,\underbrace{i_{q_{1}}}_{q_{1}},\ldots,\underbrace{i_{q_{b}}}_{q_{b}},\ldots,\tau_{L})
The second term on the right hand side in the above equation replaces $b$ empty occupations with all possible non-empty species. If the configuration $\bm{\tau}\in\widehat{\Omega}_{\ell}^{m}$ has $\ell<b$ no contributions are seen. Otherwise, if $\ell\geq b$, $b$ empties are changed, obtaining configuration with $r=\ell-b$ voids occupations, with $r\in \{0,\ldots, L-m-b\}$. Each of such a configuration is counted $\binom{L-r-m}{b}$ times. Therefore, we obtain 
	\sum_{\bm{\tau}\in \widehat{\Omega}^{m}}\Psi(\tau)=& \sum_{\ell=0}^{L-m-1}\sum_{\bm{\tau}\in \widehat{\Omega}^{m}_{\ell}}\Psi^{'}(\tau)+\Psi(N,\ldots,\underbrace{s_{1}}_{y_{1}},\ldots,\underbrace{s_{m}}_{y_{m}},\ldots,N)\\+&\sum_{b=1}^{L-m}(-1)^{b}\sum_{r=0}^{L-m-b}\binom{L-m-r}{b}\sum_{\bm{\tau}\in \widehat{\Omega}^{m}_{\ell}}\Psi^{'}(\bm{\tau})
In the second term we exchange the summations obtaining 
\sum_{\ell=0}^{L-m-1}\sum_{\bm{\tau}\in \widehat{\Omega}^{m}_{\ell}}\Psi^{'}(\tau)+\sum_{\ell=1}^{L-m-1}\sum_{b=1}^{L-\ell}(-1)^{b}\binom{L-m-\ell}{b}\sum_{\bm{\tau}\in \widehat{\Omega}^{m}_{\ell}}\Psi^{'}(\bm{\tau})
Using the Binomial theorem, for every $\ell\in \{0,\ldots, L-m-b\}$, we have that
	1+\sum_{b=1}^{L-m-\ell}(-1)^{b}\binom{L-m-\ell}{b}=0
thus, we obtain 
\sum_{\bm{\tau}\in \widehat{\Omega}^{m}}\Psi(\tau)=\Psi(N,\ldots,\underbrace{s_{1}}_{y_{1}},\ldots,\underbrace{s_{m}}_{y_{m}},\ldots,N)
that implies 
\langle n^{y_{1}}_{s_{1}}\cdots n^{y_{m}}_{s_{m}}\rangle_{\text{stat}}=\Psi(N,\ldots,\underbrace{s_{1}}_{y_{1}},\ldots,\underbrace{s_{m}}_{y_{m}},\ldots,N)
% Consider $m$ particles of non-empty types $s_{i}\in\{1,\ldots,N-1\}$ in positions $y_{i}\in\{1,\ldots,L\}$ such that $y_{i}<y_{i+1}$ for all $i=1,\ldots,m$. We aim to compute the non-equilibrium stationary state correlation $\langle n_{s_{1}}^{y_{1}}\cdots n_{s_{m}}^{y_{m}} \rangle_{stat}$. By using duality, we showed in \eqref{CorrelationByABS-prob} that
% \begin{equation}
 %	\langle n_{s_{1}}^{y_{1}}\cdots n_{s_{m}}^{y_{m}} \rangle_{stat}=\langle\hat{\bm{\xi}}\rangle_{stat,dual}
% \end{equation} 
%where $\langle\hat{\bm{\xi}}\rangle_{stat,dual}$ we have denoted the stationary state of the dual process starting from the configuration $\hat{\bm{\xi}}$. 
Using formula \eqref{ABS} we obtain 
 \Psi(N,\ldots,\underbrace{s_{1}}_{y_{1}},\ldots,\underbrace{s_{m}}_{y_{m}},\ldots,N)=\sum_{c_{1}=0}^{1}\ldots\sum_{c_{L}=0}^{1}\frac{\Gamma(2+L-\sum_{a=1}^{m}c_{k})}{\Gamma(2+L)}\prod_{k=1}^{m}\lambda_{\tau_{k}}^{c_{k}}\beta_{\tau_{k}}^{1-c_{k}}\left(2+L-y_{k}-\sum_{j=k}^{m}c_{j}\right)^{c_{k}}\dt

@@

\textbf{Remark}: the first and second cumulants, computed in \eqref{one-pts-corr} and \eqref{two-pts-corr} respectively, match with the ones found in Subsection 4.3 of \cite{vanicat2017exact}.
